Markov Model

### 2025-11-25 analysis/data-analysis.qmd
Update

---
title: "Analysis plan"
format:
  html:
    toc: false
bibliography: manuscript/references.bib
csl: manuscript/csl/apa.csl
editor:
  markdown:
    wrap: 80
---

>>>>

---
title: "Analysis plan"
format:
  html:
    toc: false
bibliography: ../manuscript/references.bib
csl: ../manuscript/csl/apa.csl
editor:
  markdown:
    wrap: 80
---

### 2025-11-25 analysis/discrete-markov.qmd
Update

# Plotting ---------------------------------------------------------------------
ggplot(data = age_cohots, aes(x = Total_p, y = prob,
                              group = interaction(Age, status_prev, status),
                              colour = label)) +
  geom_line(aes(linewidth = label)) +
  ggrepel::geom_text_repel(
    data = label_data,
    aes(label = paste0("Age ", Age), colour = as.character(Age)),
    direction = "y", nudge_x = 4, hjust = 0,
    segment.size = 0.5, segment.colour = "grey50",
    size = 3, show.legend = FALSE) +
  scale_x_continuous(
    breaks = seq(0, 60, by = 10),
    sec.axis = sec_axis( ~., name = "Previous State", breaks = NULL, labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis( ~ ., name = "Current State", breaks = NULL, labels = NULL)) +
  scale_colour_manual(values = c(
    "70"    = "#E69F00",
    "80"    = "#56B4E9",
    "90"    = "#009E73",
    "Other" = "grey80")) +
  scale_linewidth_manual(values = c(
    "70"    = 1.5,
    "80"    = 1.5,
    "90"    = 1.5,
    "Other" = 0.5)) +
  labs(
    # title = "Predicted transition probabilities for different age cohorts",
    x = "Procrastination", y = "Probability", colour = NULL) +
  facet_grid(status ~ status_prev, labeller = labeller(
    status = c("Normal Cognition" = "Normative Cognitive Function"),
    status_prev = c("Normal Cognition" = "Normative Cognitive Function")
  )) +
  theme_clean() +
  theme(
    panel.grid = element_blank()
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none")
```

>>>>

# Plotting ---------------------------------------------------------------------
ggplot(data = age_cohots, aes(x = Total_p, y = prob,
                              group = interaction(Age, status_prev, status),
                              colour = label)) +
  geom_line(aes(linewidth = label)) +
  ggrepel::geom_text_repel(
    data = label_data,
    aes(label = paste0("Age ", Age), colour = as.character(Age)),
    direction = "y", nudge_x = 4, hjust = 0,
    segment.size = 0.5, segment.colour = "grey50",
    size = 3, show.legend = FALSE) +
  scale_x_continuous(
    breaks = seq(0, 60, by = 10),
    sec.axis = sec_axis( ~., name = "Previous State", breaks = NULL, labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis( ~ ., name = "Current State", breaks = NULL, labels = NULL)) +
  scale_colour_manual(values = c(
    "70"    = "#E69F00",
    "80"    = "#56B4E9",
    "90"    = "#009E73",
    "Other" = "grey80")) +
  scale_linewidth_manual(values = c(
    "70"    = 1.5,
    "80"    = 1.5,
    "90"    = 1.5,
    "Other" = 0.5)) +
  labs(
    # title = "Predicted transition probabilities for different age cohorts",
    x = "Procrastination", y = "Probability", colour = NULL) +
  facet_grid(status ~ status_prev, labeller = labeller(
    status = c("Normal Cognition" = "Normative Cognitive Function"),
    status_prev = c("Normal Cognition" = "Normative Cognitive Function")
  )) +
  theme_clean() +
  theme(
    panel.grid = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none")
```
